Full-depth Coadds of the WISE and First-year NEOWISE-Reactivation Images

### 2016-02-28 ms.tex
first pass at results overview section

\begin{itemize}
\item We include all publicly available NEOWISER W1 and W2 exposures, 
approximately doubling the number of input L1b frames.
\item We adopt custom zero points based on repeat photometry at the ecliptic 
poles. In contrast, the \cite{lang14} unWISE processing adopted zero points 
based on the L1b header metadata.
\item We explicitly reject exposures contaminated by the Moon and/or solar 
system planets. No such rejection was included in the original unWISE W1/W2 
coadds, although these and other artifacts were addressed to some extent via 
general-purpose outlier rejection measures.
\item In this work we attempt to recover Moon-affected frames by applying 
polynomial background level corrections to the contaminated exposures.
\end{itemize}

The outputs generated in this work follow the same data model as those of 
\cite{lang14}. For each tile, a stacked image is created, plus auxiliary
maps of useful quantities such as the per-pixel inverse variance and integer 
coverage. Both our full-depth stacks and those of \cite{lang14} have units of 
Vega nanomaggies.

@@

>>>>

\begin{itemize}
\item We include all publicly available NEOWISER W1 and W2 exposures, 
approximately doubling the number of input L1b frames relative to \cite{lang14}.
\item We adopt custom zero points based on repeat photometry at the ecliptic 
poles. In contrast, the \cite{lang14} unWISE processing adopted zero points 
based on the L1b header metadata.
\item We explicitly reject exposures contaminated by the Moon and/or solar 
system planets. No such rejection was included in the \cite{lang14} unWISE 
W1/W2 coadds, although these and other artifacts were addressed to some extent 
via general-purpose outlier rejection.
\item In this work we attempt to recover Moon-affected frames by applying 
polynomial background level corrections to the contaminated exposures.
\end{itemize}

The outputs generated in this work follow the same data model as those of 
\cite{lang14}. For each tile, a stacked image is created, plus auxiliary
maps of useful quantities such as the per-pixel inverse variance and integer 
coverage. Like those of \cite{lang14}, our coadds have units of Vega 
nanomaggies.

@@

Figures 4 and 5 show large-scale renderings of our full-depth coadds 
over the north and south Galactic caps respectively. It is 
apparent that the Moon contamination has been completely eliminated in
W1 and dramatically reduced in W2. It is possible that simply folding in 
additional NEOWISER W2 frames from forthcoming data releases will diminish the 
remaining Moon imprint to such an extent that no additional processing 
modifications will be required to address this issue.

Figure 6 shows zoom-ins of low ecliptic latitude fields which illustrate
visually the reduction in statistical noise which has been achieved
by doubling the number of input exposures.

Given that we imposed various cuts to eliminate time-dependent artifacts,
it is reasonable to ask whether we have created any zero-coverage holes
as a result. We have checked all 18,240 of our integer coverage maps, and find
that every pixel has $\ge$18 epochs in W1 and $\ge$15 epochs in W2.
